---
title: "Assignment 1"
subtitle: "Intro to Programming in R"
output:
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
require(learnr)
tutorial_options()
knitr::opts_chunk$set(echo = FALSE)
```


Questions 1 and 3 are based on material not covered in class, but rather require reading Chapters 4 and 8 in R for Everyone.

Hit the "Run Code" button for every exercise to view your output. **You must run your code to confirm your final answer to each exercise in order for the code to be registered in your assignment submission.** You can re-write run the code as many times as you want. Only the last instance will be saved as your answer.

At the end of the document, remember to generate your solution hash (a text code containing all of your assignment responses) and submit it on Canvas. Submitting that hash code on Canvas is the only way to submit your assignment.

## Question 1

### Part 1

You may only submit your answer once for this question.

```{r q1-1}
question_checkbox(
  text = "What are the four main data types in R? Choose all four that apply.",
  answer("numeric", T),
  answer("integer"),
  answer("complex"),
  answer("character", T),
  answer("date", T),
  answer("logical", T),
  answer("vector"),
  answer("dataframe"),
  answer("table"),
  answer("tibble"),
  random_answer_order = TRUE
)
```

```{r q1-setup}
mysteryVar <- "27"
```

### Part 2

Replace the underscore blanks below with the correct function to determine whether or not the variable `mysteryVar` is **logical**. Your code should output `TRUE` or `FALSE`.

```{r q1-2a, exercise = TRUE, exercise.setup = "q1-setup"}
___(mysteryVar)
```

```{r q1-2a-solution}
is.logical(mysteryVar)
```

Replace the underscore blanks below with the correct function to determine whether or not the variable `mysteryVar` is **numeric**. Your code should output `TRUE` or `FALSE`.

```{r q1-2b, exercise = TRUE, exercise.setup = "q1-setup"}
___(mysteryVar)
```

```{r q1-2b-solution}
is.numeric(mysteryVar)
```

Replace the underscore blanks below with the correct function to determine whether or not the variable `mysteryVar` is **character**. Your code should output `TRUE` or `FALSE`.

```{r q1-2c, exercise = TRUE, exercise.setup = "q1-setup"}
___(mysteryVar)
```

```{r q1-2c-solution}
is.character(mysteryVar)
```

Replace the underscore blanks below with the correct function to output the type of the variable `mysteryVar`. Your code should output a character string describing the type of the variable. This answer should be consistent with the answers you got for the previous questions.

```{r q1-2d, exercise = TRUE, exercise.setup = "q1-setup"}
___(mysteryVar)
```

```{r q1-2d-solution}
class(mysteryVar)
```

## Question 2

Create a vector of numbers from one to ten called `numVec`. Use the sum function to calculate the sum of this vector.

```{r q2, exercise = TRUE}
numVec <- ___

```

## Question 3

Write a function that has two arguments. If the first argument is greater than or equal to the second argument, return the sum of the numbers. If the second argument is greater than the first argument, return the product of the numbers.

```{r q3, exercise = TRUE}
thisFunction <- function () {
  
}

# Do not edit these lines below #
# These are to help you check that your function works as intended #
# Make sure the 3 outputs look like what you expect when you run the exercise code! #
thisFunction(10, 20)
thisFunction(20, 20)
thisFunction(10, 10)
```

## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode}
learnrhash::encoder_ui(ui_before = learnrhash::default_ui(url = "https://courseworks2.columbia.edu/courses/140180/assignments/673020"))
```
