---
title: "Assignment 2"
subtitle: "Intro to Programming in R"
output:
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
require(dplyr)
require(ggplot2)
require(learnr)
tutorial_options(exercise.reveal_solution = FALSE)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

watermark <- function (x, y) {
  annotate("text",
           x = x, y = y,
           label = "FOR COMPARISON!",
           size = rel(10),
           color = "firebrick",
           angle = -45,
           alpha = 0.8)
}
```

## Intro

This homework assignment asks you to practice **plotting and data manipulation.** It requires the use of two new datasets, `starwars` and `flights`, which live in the `dplyr` and `nycflights13` packages respectively.

We have already pre-loaded the packages for you, so you will not need to `library()` them, but you will still need to use correct syntax to access the `starwars` and `flights` dataframes.

Each question comes with a pre-rendered solution output or graph against which you can compare your results. Unless otherwise indicated, you should expect that a correct code solution produces _identical_ output to the solution output shown (minus the graph watermark). If your code produces warning messages, that is okay as long as the output still looks identical to the solution output.

Hit the "Run Code" button for every exercise to view your output. **You must run your code to confirm your final answer to each exercise in order for the code to be registered in your assignment submission.** You can re-write run the code as many times as you want. Only the last instance will be saved as your answer.

At the end of the document, remember to generate your solution hash (a text code containing all of your assignment responses) and submit it on Canvas. Submitting that hash code on Canvas is the only way to submit your assignment.

## Question 1

Create a scatter plot of `starwars` characters' heights (x-axis) against their masses (y-axis), with axis labels and graph title as shown on the solution graph. (Please copy the axis labels and title verbatim.)

```{r, warning = FALSE}
dplyr::starwars %>% 
  ggplot(aes(x = height, y = mass)) +
  geom_point() +
  watermark(175, 750) +
  labs(x = "Character height (cm)",
       y = "Character mass (kg)",
       title = "Scatterplot of Star Wars characters' mass by height")
```

```{r q1, exercise = TRUE}

```

## Question 2

Create a histogram of birth year of `starwars` characters' _negative_ birth year. The units are in years before Episode 4, so you must flip the sign to plot the histogram so that the oldest characters' birth years will appear on the left. Include axis labels and graph title as shown on the solution graph. (Again, please copy the axis labels and title verbatim.)

```{r}
dplyr::starwars %>% 
  ggplot(aes(x = -birth_year)) +
  geom_histogram() +
  watermark(-400, 7) +
  labs(x = "Character birth year (years before Episode)",
       y = "# of characters",
       title = "Yoda is the outlier on this histogram")
```

```{r q2, exercise = TRUE}

```

## Question 3

Create density plots of Star Wars characters' heights, faceted by character gender. Change the fill in every density subplot to the color "skyblue". Use the theme `theme_bw()`. Set the y-axis scale on each subplot to vary freely. Label the x-axis and y-axis as shown in the solution graph. (Again, please copy the axis labels verbatim.)

```{r}
dplyr::starwars %>% 
  ggplot(aes(x = height)) +
  geom_density(fill = "skyblue") +
  facet_wrap(~gender, scales = "free_y") +
  labs(x = "Character height (cm)",
       y = "Density (Probability units)",
       title = "FOR COMPARISON!",
       subtitle = "(You can omit this title from your graph)") +
  theme_bw()
```

```{r q3, exercise = TRUE}

```

## Question 4

Filter the Star Wars data for only characters of species type "Human", "Droid", or "Wookiee". Then, create a violin plot of characters' heights by species. Use the Economist theme in the `ggthemes` package. Label the x-axis, y-axis, and title as shown in the solution graph. (Again, please copy the axis labels and title verbatim.)

```{r}
dplyr::starwars %>% 
  filter(species %in% c("Human", "Droid", "Wookiee")) %>% 
  ggplot(aes(x = species, y = height)) +
  geom_violin() +
  watermark(2, 160) +
  labs(x = "Character species",
       y = "Character height (cm)",
       title = "Star Wars character heights from 3 species") +
  ggthemes::theme_economist()
```

```{r q4, exercise = TRUE}

```

## Question 5

These questions will use the `flights` dataset. In each exercise, you will need to fill the marked blanks with code. You will not need to add functions outside of those that are already marked with placeholders for you, but you may sometimes need to put multiple statements inside one set of function parentheses.

The solution outputs are capped at 1000 rows, so if your solution comes out to have more than 1000 rows but the first several rows look identical, your code should still be correct.

Read Chapter 12 if you are uncertain about these functions.

```{r flights-setup}
require(nycflights13)
```

### Part 1

Use the `contains()` function to select columns from the `flights` dataset that contain the word "dep".

```{r}
nycflights13::flights %>% 
  select(contains("dep"))
```

```{r q5-1, exercise = TRUE, exercise.setup = "flights-setup"}
flights %>%
  ___(___)
```

### Part 2

Use `starts_with()` to select columns that start with the letter "s". 

```{r}
nycflights13::flights %>% 
  select(starts_with("s"))
```

```{r q5-2, exercise = TRUE, exercise.setup = "flights-setup"}
flights %>%
  ___(___)
```

## Question 6

Group the `flights` data by origin airport, and then calculate the mean and standard deviation of `dep_delay`, `arr_delay`, `air_time` and `distance` for each origin, ignoring any `NA` values. Use any suitable method to make your summary column names identical to the summary columns in the solution output. Chapter 4 discusses ways to deal with `NA`s.

```{r}
nycflights13::flights %>% 
  group_by(origin) %>% 
  summarize(across(c(dep_delay, arr_delay, air_time, distance),
                   list(mean = mean, sd = sd), 
                   na.rm = T))
```

```{r q6, exercise = TRUE, exercise.setup = "flights-setup"}
flights %>%
  ___(___) %>% 
  ___(___)
```

## Question 7

Use `filter()` to return rows from the `flights` data that originate from JFK and depart (actual, not scheduled time) later than 12:00 pm and earlier than 9:00 pm.

```{r}
nycflights13::flights %>% 
  filter(origin == "JFK", dep_time > 1200, dep_time < 2100)
```

```{r q7, exercise = TRUE, exercise.setup = "flights-setup"}
flights %>%
  filter(___)
```

## Question 8

Create a new column in the flights dataset showing the average speed for each flight, calculated as `distance` divided by `air_time`. Name the column `speed`. Use this column to calculate the average speed for flights departing each NYC origin airport, ignoring any `NA` values. Name that summary column `avg_speed`.

```{r}
nycflights13::flights %>% 
  mutate(speed = distance / air_time) %>% 
  group_by(origin) %>% 
  summarize(avg_speed = mean(speed, na.rm = T))
```

```{r q8, exercise = TRUE, exercise.setup = "flights-setup"}
flights %>%
  ___(speed = ___) %>% 
  ___(___) %>% 
  ___(avg_speed = ___)
```

## Submit

```{r context="server"}
learnrhash::encoder_logic(strip_output = TRUE)
```

```{r encode}
learnrhash::encoder_ui(ui_before = learnrhash::default_ui(url = "https://courseworks2.columbia.edu/courses/140180/assignments/673024"))
```
